Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-09-19 paper/paper.tex
Move Dataset to back matter
Edit dataset section

\section{Dataset} \label{sec:dataset}

The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of 16 different musical instruments played with different playing techniques, which leads to 235 different couple of instrument / playing technique. For each couple, the pitch and intonation is varied leading to 25444 audio samples.

The recorded instruments belongs to the wind and string classes. For winds, the instruments considered in the second experiment are: accordion (Acc), saxophone alto (ASax), tuba (Tb), bassoon (Bn), clarinet Bb (BbCl), flute (Fl), horn (Hn), oboe (Ob), trombone tenor (TTbn), and trumpet C (TpC). For the string class, the instruments are: guitar (Gtr), harp (Hp), viola (Va), violin (Vn), violoncello (Vc), and contrabass (Cb).

Some instruments can be complemented with sordina (S), wha (W). The addition of this kind of device modifying the shape of the instrument, a saxophone alto and saxophone alto with sordina are considered as different instruments.
\vl{This is crucial and should not be deferred to the appendix. @writing}
\ml{J'ai mis ca en appendice pour ne pas que le lecteur confonde la base SOL complete et les données considérées dans l'étude.}

\vl{A bubble plot of number of notes per instrument (x axis) and playing technique
(y axis) would be extremely useful. @data @figure}
\ml{Tu voudrais ca pour la base SOL complete ou les données considérées dans l'étude ?}
\vl{Les donn\'{e} de l'\{e}tude, relatives aux Figures 5 et 6.\}

@@

>>>>

@@

%% Appendices

\section*{Dataset}
\label{sec:dataset}

The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of $16$ different musical instruments played with different PTs, which leads to $235$ different IPT pairs.
In addition, the pitch and nuance is varie for each pair (when applicable), yielding a total of $25444$ audio recordings.
For each couple, the pitch and intonation is varied leading to 25444 audio samples.

The recorded instruments belongs to the wind and string classes.
For winds, the instruments considered in the second experiment are: accordion (Acc), saxophone alto (ASax), tuba (Tb), bassoon (Bn), clarinet Bb (BbCl), flute (Fl), horn (Hn), oboe (Ob), trombone tenor (TTbn), and trumpet C (TpC).
For the string class, the instruments are: guitar (Gtr), harp (Hp), viola (Va), violin (Vn), violoncello (Vc), and contrabass (Cb).
\ja{Better to display these in a table?}

Some instruments can be complemented with sordina (S), wha (W).
The addition of this kind of device modifies the shape of the instrument.
Consequently, an alto saxophone and alto saxophone with sordina are considered as different instruments.
\vl{This is crucial and should not be deferred to the appendix. @writing}
\ml{J'ai mis ca en appendice pour ne pas que le lecteur confonde la base SOL complete et les données considérées dans l'étude.}

\vl{A bubble plot of number of notes per instrument (x axis) and playing technique
(y axis) would be extremely useful. @data @figure}
\ml{Tu voudrais ca pour la base SOL complete ou les données considérées dans l'étude ?}
\vl{Les donn\'{e} de l'\'{e}tude, relatives aux Figures 5 et 6.}
